NN_Accel_Heading

### 2024-03-08 Fish Data Analysis/NN_Accel_Heading.qmd
Saving here before more messing around

@@

```{r}
raw_new <- read.csv("Data/Fish_Comp_Values_3D.csv")
raw_old <- read.csv("Data/older_Fish_Comp_Values_3D.csv") %>% mutate(Angle = deg2rad(Angle),
                                                                     Fish1_Yaw_Heading = deg2rad(Fish1_Yaw_Heading),
                                                                     Fish1_Yaw_Heading_PS = deg2rad(Fish1_Yaw_Heading_PS))

hist(raw_new$Angle - deg2rad(raw_old$Angle))
hist(raw_new$Fish1_Yaw_Heading - deg2rad(raw_old$Fish1_Yaw_Heading))
hist(raw_new$Fish1_Yaw_Heading_PS - deg2rad(raw_old$Fish1_Yaw_Heading_PS))

@@

fish_data_nn <- fish_comp_data_combo %>% group_by(Fish1,Tailbeat_Num,Data_ID) %>%
                                    mutate(nndDistance = min(Distance, na.rm = TRUE),
                                           nndDistance = ifelse(is.infinite(nndDistance), NA, nndDistance),
                                           all_nas = all(is.na(nndDistance))) %>%
                                    filter(Distance == nndDistance | all_nas) %>%
                                    mutate(row_n = row_number()) %>%
                                    filter(row_n == 1) %>%
                                    ungroup() %>%
                                    mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS) %>%
                                    filter(Distance <= 2)

@@

nn_heading_sum <- fish_data_nn_normal %>% mutate(angle_bins = round_any(Angle,pi/6)) %>%
                                                group_by(angle_bins,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
                                                summarise(mean_turn = mean(Fish1_Yaw_Heading_PS, na.rm = T),
                                                          sd_turn = sd(Fish1_Yaw_Heading_PS, na.rm = T),
                                                          n = n()) %>%
                                                ungroup() %>%
                                                na.omit()

nn_accel_sum <- fish_data_nn_normal %>% mutate(distance_bins = round_any(Relative_X,0.25)) %>%
                                                group_by(distance_bins,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
                                                summarise(mean_accel = mean(Fish1_Accel, na.rm = T),
                                                          sd_accel = sd(Fish1_Accel, na.rm = T),
                                                          n = n()) %>%
                                                ungroup() %>%
                                                na.omit()

@@

@@

tester_model <- lm(Fish1_Yaw_Heading_PS ~ sin(Angle):Ablation:Darkness, data = fish_data_nn_model) 
Anova(tester_model)

ggplot(fish_data_nn %>% filter(Flow == "Still Water"),
       aes(x = Angle, y = Fish1_Yaw_Heading_PS, color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point(alpha = 0.1)+
  facet_wrap(~ interaction(Ablation, Darkness, sep =", ")) +
  #geom_smooth(se = F)+
  #geom_smooth(se = F, method = glm, formula = y ~ 1)+
  geom_line(aes(y = predict(heading_ps_angle_step)), size = 1)+
  theme_classic() +
  #ylim(-5,5)+
  xlab("direction of neighbour (degrees)") +
  ylab("focal fish turning angle (rad/sec)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  scale_x_continuous(breaks = unique(nn_heading_sum$angle_bins),
                     labels = rad2deg(unique(nn_heading_sum$angle_bins))) +
  labs(color = "Sensory Conditions")

ggplot(nn_heading_sum %>% filter(Flow == "Still Water"),
       aes(x = angle_bins, y = rad2deg(mean_turn), color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point()+
  #geom_smooth(se = F)+
  #geom_line(aes(y = sin_pred)) +
  #geom_line(alpha = 0.75) +
  #geom_smooth(se = F, method = glm, formula = y ~ sin(x))+
  geom_line(aes(y = rad2deg(predict(tester_model,
                    newdata = nn_heading_sum %>% filter(Flow == "Still Water") %>% mutate(Angle = angle_bins)))), size = 1)+
  theme_classic() +
  ylim(-50,50) +
  xlab("direction of neighbour (degrees)") +
  ylab("focal fish turning angle (degrees/sec)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  scale_x_continuous(breaks = unique(nn_heading_sum$angle_bins),
                     labels = rad2deg(unique(nn_heading_sum$angle_bins))) +
  # scale_x_continuous(breaks = unique(nn_heading_sum$angle_bins),
  #                    labels = c("-π","-3π/4","-π/2","-π/4","0","π/4","π/2","3π/4","π"))+
  labs(color = "Sensory Conditions")

# emmeans(tester_model, ~ Ablation|Darkness, type = "response")
# emmeans(tester_model, ~ Darkness|Ablation, type = "response")

>>>>

nth_min <- function(x,n){sort(na.omit(x))[n]}

@@

@@

fish_data_nn <- fish_comp_data_combo %>% group_by(Fish1,Tailbeat_Num,Data_ID) %>%
                                    mutate(#nndDistance = min(Distance, na.rm = TRUE),
                                           nndDistance = nth_min(Distance, 1),
                                           nndDistance = ifelse(is.infinite(nndDistance), NA, nndDistance),
                                           all_nas = all(is.na(nndDistance))) %>%
                                    filter(Distance == nndDistance | all_nas) %>%
                                    mutate(row_n = row_number()) %>%
                                    filter(row_n == 1) %>%
                                    ungroup() %>%
                                    mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS) %>%
                                    filter(Distance <= 1.5)

@@

nn_heading_sum <- fish_data_nn_normal %>% mutate(angle_bins = round_any(Angle,pi/5)) %>%
                                                group_by(angle_bins,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
                                                summarise(mean_turn = mean(Fish1_Yaw_Heading_PS, na.rm = T),
                                                          sd_turn = sd(Fish1_Yaw_Heading_PS, na.rm = T),
                                                          n = n()) %>%
                                                ungroup() %>%
                                                na.omit()

nn_accel_sum <- fish_data_nn_normal %>% mutate(distance_bins = round_any(Relative_X,0.2)) %>%
                                                group_by(distance_bins,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
                                                summarise(mean_accel = mean(Fish1_Accel, na.rm = T),
                                                          sd_accel = sd(Fish1_Accel, na.rm = T),
                                                          n = n()) %>%
                                                ungroup() %>%
                                                na.omit()

@@

Estimating functions

```{r}
#par 1 = amp
#par 2 = freq
#par 3 = phase

min.RSS <- function(data, par) {
             with(data, sum(par[1]*sin(2*pi/par[2]*Angle+par[3]) - Fish1_Yaw_Heading_PS)^2)
}

result_F0LNDN <- optim(par = c(1, 1, 0), fn = min.RSS, data = fish_data_nn_normal %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Light"))
result_F0LYDN <- optim(par = c(1, 1, 0), fn = min.RSS, data = fish_data_nn_normal %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Light"))
result_F0LNDY <- optim(par = c(1, 1, 0), fn = min.RSS, data = fish_data_nn_normal %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Dark"))
result_F0LYDY <- optim(par = c(1, 1, 0), fn = min.RSS, data = fish_data_nn_normal %>% filter(Flow_Ablation_Darkness == "Still Water, Ablated, Dark"))

result_F0LNDN$par
result_F0LYDN$par
result_F0LNDY$par
result_F0LYDY$par
```

@@

manual_model <- lm(Fish1_Yaw_Heading_PS ~ sin(Angle) + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness, 
                   data = fish_data_nn_model) 
Anova(manual_model)

#Raw data
ggplot(fish_data_nn %>% filter(Flow == "Still Water"),
       aes(x = Angle, y = Fish1_Yaw_Heading_PS, color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point(alpha = 0.1)+
  facet_wrap(~ interaction(Ablation, Darkness, sep =", ")) +
  geom_line(aes(y = predict(heading_ps_angle_step)), size = 1)+
  theme_classic() +
  xlab("direction of neighbour (degrees)") +
  ylab("focal fish turning angle (rad/sec)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  scale_x_continuous(breaks = unique(nn_heading_sum$angle_bins),
                     labels = rad2deg(unique(nn_heading_sum$angle_bins))) +
  labs(color = "Sensory Conditions")

#Means graph
ggplot(nn_heading_sum %>% filter(Flow == "Still Water"),
       aes(x = angle_bins, y = rad2deg(mean_turn), color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point()+
  geom_line(aes(y = rad2deg(predict(manual_model,
                    newdata = nn_heading_sum %>% filter(Flow == "Still Water") %>% mutate(Angle = angle_bins)))), size = 1)+
  theme_classic() +
  ylim(-50,50) +
  xlab("direction of neighbour (degrees)") +
  ylab("focal fish turning angle (degrees/sec)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  scale_x_continuous(breaks = unique(nn_heading_sum$angle_bins),
                     labels = rad2deg(unique(nn_heading_sum$angle_bins))) +
  labs(color = "Sensory Conditions")

test(emmeans(manual_model, pairwise ~Ablation*Darkness | Angle, at = list(Angle = c(pi/2))))
